Ensemble Stability of Biological Networks

### 2014-09-15 paper.tex
add figure to demonstrate system composed of modules

For the case of continuous deterministic observables, the above process can be made more precise by associating a manifold to each observable, a directed graph to the interdependencies, and a vector field satisfying these interdependencies for each observable over the space determined by taking the product of the manifolds associated to the collection of observables \cite{Deville}. For example, if we have two observables $\{x_1,x_2\}$ where the domains in which they are quantified are given by manifolds $\{M_1,M_2\}$ such that $x_1 \in M_1 \equiv \mathbb{R}^1$ and $x_2 \in M_2 \equiv \mathbb{R}^1$, a directed graph $G_X$ describing the dependencies between these observables and vector field $V$ with components $\{F_1,F_2\}$ defined on $M_1 \otimes M_2 \equiv \mathbb{R}^2$ satisfying the dependencies determined by $G_X$. If the system under consideration has the graph
\begin{center}
\input{tex/examplehamdyngraph}
\end{center}
with adjacency matrix
$$
\adj(G_X) = \begin{pmatrix}
0 & 1 \\
1 & 1
\end{pmatrix}
$$
then for the system $X = \{G_X, M_X, F_X\}$, where $M_X \equiv \{M_1,M_2\}$ and $F_X \equiv \{F_1,F_2\}$ such that $F_1$ is constrained to be a function of $x_2$ and $F_2$ is a function of both $x_1$ and $x_2$ yielding the flow equations
\begin{align*}
\frac{dx_1}{dt} & = F_1(x_2)\\
\frac{dx_2}{dt} & = F_2(x_1,x_2)
\end{align*}

>>>>

For the case of continuous deterministic observables, the above process can be made more precise by associating a manifold to each observable, a directed graph to the interdependencies, and a vector field satisfying these interdependencies for each observable over the space determined by taking the product of the manifolds associated to the collection of observables \cite{Deville}. For example, if we have two observables $\{x_1,x_2\}$ where the domains in which they are quantified are given by manifolds $\{M_1,M_2\}$ such that $x_1 \in M_1 \equiv \mathbb{R}^1$ and $x_2 \in M_2 \equiv \mathbb{R}^1$, a directed graph $G_X$ describing the dependencies between these observables and vector field $V$ with components $\{F_1,F_2\}$ defined on $M_1 \otimes M_2 \equiv \mathbb{R}^2$ satisfying the dependencies determined by $G_X$. If the system under consideration has the graph shown in \ref{fig:examplesystemmodules}A
% \begin{center}
% \input{tex/examplehamdyngraph}
% \end{center}
with adjacency matrix
$$
\adj(G_X) = \begin{pmatrix}
0 & 1 \\
1 & 1
\end{pmatrix}
$$
then for the system $X = \{G_X, M_X, F_X\}$, where $M_X \equiv \{M_1,M_2\}$ and $F_X \equiv \{F_1,F_2\}$ such that $F_1$ is constrained to be a function of $x_2$ and $F_2$ is a function of both $x_1$ and $x_2$ yielding the flow equations
\begin{align*}
\frac{dx_1}{dt} & = F_1(x_2)\\
\frac{dx_2}{dt} & = F_2(x_1,x_2)
\end{align*}

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.6\columnwidth]{fig/examplesystemmodules.pdf}
\caption{{\bf Example of the combination of open system modules to construct closed systems.} (A) Example of combining two open modules to construct a closed system of two components (B) Analogous example for combining three open modules to construct a closed system with three components}
\label{fig:examplesystemmodules}
\end{figure}
